\begin{thebibliography}{99}

\bibitem{banikazemi2005san}
M. Banikazemi, D. Poff, and B. Abali.
Storage-based intrusion detection for Storage Area Networks (SANs).
MSST, 2005.
\url{https://research.ibm.com/publications/storage-based-intrusion-detection-for-storage-area-networks-sans}

\bibitem{allalouf2010idstor}
M. Allalouf et al.
Block storage listener for detecting file-level intrusions.
MSST, 2010.
\url{https://research.ibm.com/publications/block-storage-listener-for-detecting-file-level-intrusions}

\bibitem{baek2018ssdinsider}
S.-H. Baek et al.
SSD-Insider: Internal Defense of Solid-State Drive against Ransomware with Perfect Data Recovery.
ICDCS, 2018.
\url{https://doi.org/10.1109/ICDCS.2018.00089}

\bibitem{ibmstorage2023}
IBM Research.
Efficient ransomware detection with machine learning in storage systems.
FMS, 2023.
\url{https://research.ibm.com/publications/efficient-ransomware-detection-with-machine-learning-in-storage-systems}

\bibitem{reategui2024generalizability}
J. Reategui, R. Pletka, and P. Diamantopoulos.
On the Generalizability of Machine Learning-based Ransomware Detection in Block Storage.
arXiv:2412.21084, 2024.
\url{https://arxiv.org/abs/2412.21084}

\bibitem{deftpunk2024}
Z. Wang et al.
Ransom Access Memories: Achieving Practical Ransomware Protection in Cloud with DeftPunk.
OSDI, 2024.
\url{https://www.usenix.org/conference/osdi24/presentation/wang-zhongyu}

\bibitem{wannalaugh2024}
P. Diamantopoulos et al.
WannaLaugh: A Configurable Ransomware Emulator.
SYSTOR, 2024.
\url{https://doi.org/10.1145/3688351.3689163}

\bibitem{ransap}
M. Hirano.
RanSAP public repository.
\url{https://github.com/manabu-hirano/RanSAP}

\bibitem{hirano2021ransap}
M. Hirano et al.
RanSAP dataset and storage access pattern study.
Forensic Science International: Digital Investigation, 2021.
\url{https://doi.org/10.1016/j.fsidi.2021.301314}

\bibitem{ransmap}
M. Hirano.
RanSMAP public repository.
\url{https://github.com/manabu-hirano/RanSMAP}

\bibitem{hirano2024ransmap}
M. Hirano et al.
RanSMAP storage and memory access pattern study.
Computers \& Security, 2024.
\url{https://doi.org/10.1016/j.cose.2024.104202}

\bibitem{sniaiotta}
SNIA.
IOTTA Repository.
\url{https://www.snia.org/educational-library/iotta-repository-2019}

\bibitem{umass}
UMass Trace Repository.
Storage traces.
\url{https://traces.cs.umass.edu/docs/traces/storage/}

\bibitem{napierone}
NapierOne Dataset.
\url{https://registry.opendata.aws/napierone/}

\bibitem{kharraz2016unveil}
A. Kharraz et al.
UNVEIL: A Large-Scale, Automated Approach to Detecting Ransomware.
USENIX Security, 2016.

\bibitem{scaife2016cryptodrop}
N. Scaife et al.
CryptoLock (and Drop It): Stopping Ransomware Attacks on User Data.
ICDCS, 2016.

\bibitem{continella2016shieldfs}
A. Continella et al.
ShieldFS: A Self-healing, Ransomware-aware Filesystem.
ACSAC, 2016.

\bibitem{kharraz2017redemption}
A. Kharraz and E. Kirda.
Redemption: Real-Time Protection Against Ransomware at End-Hosts.
RAID, 2017.

\bibitem{kolodenker2017paybreak}
E. Kolodenker et al.
PayBreak: Defense against cryptographic ransomware.
AsiaCCS, 2017.

\bibitem{malhotra2016lstm}
P. Malhotra et al.
LSTM-based Encoder-Decoder for Multi-sensor Anomaly Detection.
ICML Workshop on Anomaly Detection, 2016.

\bibitem{hundman2018lstm}
K. Hundman et al.
Detecting Spacecraft Anomalies Using LSTMs and Nonparametric Dynamic Thresholding.
KDD, 2018.

\bibitem{audibert2020usad}
J. Audibert et al.
USAD: UnSupervised Anomaly Detection on Multivariate Time Series.
KDD, 2020.

\bibitem{nvme}
NVM Express.
NVM Express specifications.
\url{https://nvmexpress.org/specifications/}

\bibitem{snia-csd}
SNIA.
Computational Storage Technical Work Group.
\url{https://www.snia.org/computationaltwg}

\bibitem{mnn}
Alibaba.
MNN: A lightweight deep neural network inference engine.
\url{https://github.com/alibaba/MNN}

\end{thebibliography}
